\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Yuki Janvier \\}
\normalsize yuki@tamu.edu $\mid$ (281) 866-4650 $\mid$ www.linkedin.com/in/yuki-janvier/ $\mid$ www.github.com/yukiCodesStuff/ \\
\hrulefill
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Texas A\&M University}, College Station, TX \hfill Fall 2024 \\
\textit{B.S. in Computer Science} \hfill GPA: 3.5/4.0 \\ 
\textbf{Relevant Coursework:} Machine Learning, Cloud Computing, AWS with Go, Networks and Distributed Processing \\ 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Atlassian} \hfill Seattle, WA \\
\textit{Software Engineering Intern, Confluence Automation} \hfill May, 2024 $-$ Aug, 2024
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Rapidly developed and deployed a \textbf{highly-requested} (already used by over \textbf{10,000} users) update to Confluence Automation rules, event-driven functions that automatize common tasks, using \textbf{Spring Boot and React with TypeScript} enabling users to reference documents and spaces created within the same automation rule. }
\item {\textbf{Simplified existing data models reducing object size by roughly 90\%}, significantly reducing the size of stored automation rules and \textbf{greatly optimizing resource utilization.} }
\item {Integrated \textbf{AI rule generation} into the new feature, empowering Atlassian's AI agent to create rules using the new feature. }
\item {Successfully migrated and customized numerous React components to accommodate the new feature and its added functionality. \\}
\end{itemize}

\noindent \textbf{Frogslayer} \hfill College Station, TX \\
\textit{Junior Software Developer} \hfill October, 2023 $-$ May, 2024
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Assisted in the comprehensive overhaul of Dave and Buster's Kiosk software, significantly enhancing user and management experience and operational efficiency.}
\item {Developed robust and scalable UI components using \textbf{React with TypeScript}, improving the experience of customer-facing kiosks and the kiosk manager portal.}
\item {Implemented hardware integration solutions using the \textbf{Electron framework (C++)}, enabling seamless operations of cash dispensers, barcode scanners, and other peripherals, thereby optimizing transaction processes.}
\item {Assisted development on a secure, efficient API communication strategy using \textbf{Spring Boot and GraphQL}, facilitating real-time data exchange for critical functions such as customer analytics and coupon validation.} \\
\end{itemize}

\noindent \textbf{Atlassian} \hfill Mountain View, CA \\
\textit{Software Engineering Intern (Cloud Security), Enterprise Trust} \hfill May 2023, Year $-$ August, 2023
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Developed a \textbf{highly demanded new feature} for Atlassian Access (\textbf{requested by roughly 10 organizations per month}), enabling Access-level subscribers to temporarily manage multiple Identity Providers (IdP), \textbf{greatly increasing the transition rate to Enterprise-level subscriptions.}}
\item{Used \textbf{Spring Boot with Java and Reactive Programming} to architect a backend service that interacts with DynamoDB, determining the validity of an organization's temporary access to multiple Identity Providers (IdP) based off of business logic and their existence in the database}
\item {Implemented the frontend using \textbf{React and TypeScript}, allowing support engineers to process customer requests for the new feature. }
\item {Successfully deployed the feature, which is now being \textbf{actively requested and used} by multiple corporations (namely Intel), demonstrating immediate value and industry acceptance. \\}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECTS}} \\
\noindent \textbf{Aggie Grocer} \textit{HowdyHack 2022 Winner} \\
Created an application that generates recipes based on a user’s current inventory. Unlike currently available options, Aggie Grocer utilizes \textbf{OCR (Optical Character Recognition)} to scan receipts and automatically update a user’s inventory. Used HTML, CSS, and \textbf{JavaScript with Tesseract} to create and implement the OCR function for Aggie Grocer. \\

\noindent \textbf{PokeMock} \textit{C++ Pokemon Mock} \\
Created a mock of the famous Pok\'emon game using \textbf{C++ with the SFML2} library. The progam is enables basic game functionalities such as character movement, as well as added features such as custom map creation and generation. \\

\noindent \textbf{Commutitas} \textit{HackMIT 2023 Project} \\
Created a unique platform dedicated to fostering communal celebrations for individuals who may not have the opportunity to share holidays with their own families, creating a sense of belonging and joy during special occasions. This was created using React for the frontend, and Spring Boot for the backend. 
\end{document}
